---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# survsmart [![](https://img.shields.io/badge/WEBsite-click--me-orange.svg)](http://UBESP-DCTV/survsmart/)

<!-- badges: start -->
[![R-CMD-check](https://github.com/UBESP-DCTV/survsmart/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/UBESP-DCTV/survsmart/actions/workflows/R-CMD-check.yaml)
[![covr](https://github.com/UBESP-DCTV/survsmart/actions/workflows/covr.yaml/badge.svg)](https://github.com/UBESP-DCTV/survsmart/actions/workflows/covr.yaml)
[![lint](https://github.com/UBESP-DCTV/survsmart/actions/workflows/lint.yaml/badge.svg)](https://github.com/UBESP-DCTV/survsmart/actions/workflows/lint.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/survsmart)](https://CRAN.R-project.org/package=survsmart)
<!-- badges: end -->

The goal of survsmart is to ...

## Installation

You can install the development version of survsmart from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("UBESP-DCTV/survsmart")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval = FALSE}
library(survsmart)
## basic example code
```


## Code of Conduct

Please note that the survsmart project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.


